%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Configuration Management Intern — Wouessi Technologies}{Jan 2025 -- Apr 2025}
{Remote}{}
\resumeItemListStart
    \resumeItem{Established Git branching strategies for frontend and backend EMS teams, improving collaboration and code organization.}
    \resumeItem{Implemented structured pull request workflows and managed feature branch merges into the \texttt{main} branch, ensuring deployment readiness.}
    \resumeItem{Automated deployments through CI/CD pipelines to development servers, reducing manual release efforts and minimizing errors.}
    \resumeItem{Provided GitHub and technical workflow support to engineering teams, improving merge and release efficiency by 30\%.}
\resumeItemListEnd

\resumeSubheading
{Technician Solutions Specialist — Business Tech Ninjas}{Apr 2024 -- Sep 2024}
{Brampton, ON}{}
\resumeItemListStart
    \resumeItem{Optimized workflow automation with Flowise, reducing manual processes and enhancing operational efficiency across multiple client projects.}
    \resumeItem{Integrated AI-driven chat solutions via the ChatGPT API, improving dynamic customer interactions and client engagement metrics.}
    \resumeItem{Deployed scalable web services with Render, achieving a 20\% improvement in application response times.}
    \resumeItem{Enhanced search and recommendation systems using Pinecone’s vector database, delivering more accurate and personalized results for end-users.}
\resumeItemListEnd

\resumeSubheading
{API Integration Engineer Intern — Vosyn}{Jan 2022 -- Sep 2023}
{Brampton, ON}{}
\resumeItemListStart
    \resumeItem{Led the design and integration of APIs to align mouth movements and emotional expressions with translated audio for multilingual video synchronization.}
    \resumeItem{Architected a scalable microservices infrastructure, improving system performance and reducing data latency.}
    \resumeItem{Implemented advanced security measures including encryption, rate limiting, and input validation to protect sensitive information.}
    \resumeItem{Directed seamless third-party API integrations, resolving complex issues and ensuring smooth deployments with external partners.}
\resumeItemListEnd

\resumeSubHeadingListEnd
